My title

### 2022-04-05 outputs/paper/paper.Rmd
initial commit
initial commit for final paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ayoon Kim 
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ayoon Kim 
thanks: "Code and data are available at: LINK."
date: "27 April 2022"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
keywords: ""
output: 
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
